### 2015-05-13 evaluation.tex
update in evaluation text

We can see that \whoop reports more races than \corral. This is expected, since \whoop employs an over-approximating shared state abstraction to conservatively model the effects of additional threads when analysing an entry point pair, and because lockset analysis is inherently imprecise; both factors can lead to false alarm race reports.  On the other hand, \corral is precise, but can miss races because only a limited number of context switches are considered.  Another issue with \corral is loop coverage due to unsound loop unrolling. To tackle this, we enable the built-in loop over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false positives, but we have not seen this in practice.

\ADComment{Would this be a good point to reiterate the fact that when we apply \corral to an entry point pair, we are just checking the specific pair of threads, and are not accounting for actions by other threads?}

\ADComment{At this point, is it absolutely clear what we do with \corral?  I.e., that we consider each entry point pair separately, and do not employ any abstraction to model additional threads?}

>>>>

We can see that \whoop reports more races than \corral. This is expected, since \whoop employs an over-approximating shared state abstraction to conservatively model the effects of additional threads when analysing an entry point pair, and because lockset analysis is inherently imprecise; both factors can lead to false alarm race reports.  On the other hand, \corral is precise, but can miss races because only a limited number of context switches are considered.  Another issue with \corral is loop coverage due to unsound loop unrolling. To tackle this, we enable the built-in loop over-approximation described in~\cite{lal2014powering}. This can potentially lead \corral to report false positives, but we have not seen this in practice. Finally, when we apply \corral to a pair of entry points, we are just checking the specific pair and are not accounting for the effect of other threads (see Section~\ref{corral}); this can also cause \corral to miss some races.
